### 2018-10-29 01_introduction.tex
Bringing it down to the page limit

The above points motivate the development of scalable algorithmic
tools for such dual-arm rearrangement instances. This work considers
certain relaxations to achieve this objective. In particular,
monotone tabletop instances are considered, where the start and goal
object poses do not overlap.  Furthermore, the focus is on
synchronized execution of pick-and-place actions by the two arms. i.e., where the two arms simultaneously transfer (different) objects, or simultaneously move towards picking the next objects.
Theoretical arguments and experimental evaluation indicate that the
synchronization assumption does not significantly degrade solution
quality.

@@

The first contribution is the study of the combinatorial structure of
synchronous, monotone dual-arm rearrangement. Then, a mixed integer linear programming (\milp) model is
proposed that achieves optimal coordinated solutions in this domain.
An efficient algorithm {\tt Tour\_Over\_Matching} (\algo) is proposed
that significantly improves in scalability. \algo\ first optimizes the
cost of object transfers and assigns objects to the two arms by
solving an optimal matching problem. It minimizes the cost of
moves from an object's goal to another object's start pose per
arm as a secondary objective by employing a {\tt TSP} solution. Most
of the computation time is spent on the many calls to a
lower-level motion planner that coordinates the two arms. A lazy
evaluation strategy is proposed, where candidate solution sequences
are developed first and then motion plans are evaluated for them. The
strategy results in significant computational improvement and
minimizes the calls to the coordination motion planner.  An analysis
is also performed on the expected improvement in solution quality
versus the single arm case, as well as the expected cost overhead from a
synchronous solution.

Finally, experiments for i) a simple planar picker setting, and ii) a
model of two 7-DOF Kuka arms, demonstrate a nearly two-fold
improvement against the single arm case for the proposed approach in practice. The
solutions are close to optimal for the dual-arm case and the algorithm
exhibits good scalability. The computational costs of both the optimal
and the proposed method are significantly improved from the lazy
evaluation strategy. 
% When the synchronous solutions are smoothed to
% asynchronous ones, there is not significance difference in overall
% path quality. \kiril{This statement is unclear. What is the benefit from performing this step?}

>>>>

The above points motivate the development of scalable algorithmic
tools for such dual-arm rearrangement instances. This work considers
certain relaxations to achieve this objective. In particular,
monotone tabletop instances are considered, where the start and goal
object poses do not overlap.  Furthermore, the focus is on
synchronized execution of pick-and-place actions by the two arms. i.e., where the two arms simultaneously transfer (different) objects, or simultaneously move towards picking the next objects.
Theoretical arguments and experimental evaluation indicate that this does not significantly degrade solution
quality.

@@

The first contribution is the study of the combinatorial structure of
synchronous, monotone dual-arm rearrangement. Then, a mixed integer linear programming (\milp) model is
proposed that achieves optimal coordinated solutions in this domain.
The proposed efficient algorithm {\tt Tour\_Over\_Matching} (\algo) significantly improves in scalability. \algo\ first optimizes the
cost of object transfers and assigns objects to the two arms by
solving an optimal matching problem. It minimizes the cost of
moves from an object's goal to another object's start pose per
arm as a secondary objective by employing a {\tt TSP} solution. Most
of the computation time is spent on the many calls to a
lower-level motion planner that coordinates the two arms. A lazy
evaluation strategy is proposed, where motion plans are evaluated for candidate solution sequences. This results in significant computational improvement and
reduces the calls to the motion planner.  An analysis
studies the expected improvement in solution quality
versus the single arm case, as well as the expected cost overhead from a
synchronous solution.

Finally, experiments for i) a simple planar picker setting, and ii) two 7-DOF Kuka arms, demonstrate a nearly two-fold
improvement against the single arm case for the proposed approach in practice. The algorithm exhibits close to optimal solutions and good scalability. 
The lazy evaluation strategy significantly improves computation costs for both the optimal and proposed methods.
%The computational costs of both the optimal
%and the proposed method are significantly improved from the lazy
%evaluation strategy. 
% When the synchronous solutions are smoothed to
% asynchronous ones, there is not significance difference in overall
% path quality. \kiril{This statement is unclear. What is the benefit from performing this step?}

### 2018-10-29 04_baseline.tex
Bringing it down to the page limit

\vspace{-0.25in}
\begin{equation*}
{\permu[n]{2}} + {\permu[n]{2}}\times{\permu[n-2]{2}} + ... + {\permu[n]{2}}\times{\permu[n-2]{2}}\times{\permu[n-4]{2}}...\times{\permu[2]{2}} =\sum_{L=1}^{n/2} {\ \prod_{k=0}^{2L-1}{(n-k)}},
\vspace{-0.15in}
\end{equation*}
where $\permu[n]{k}$ denotes the number of $k$-permutations of $n$.

\begin{wrapfigure}{r}{2.4in}
    \vspace{-.1in}
	\centering
	\includegraphics[width=2.3in]{figures/dual_backtracking.PNG}
    \vspace{-.15in}
	\caption{Search tree for 4 objects. In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. }
	\label{fig:backtracking}
    \vspace{-.3in}
\end{wrapfigure}
Motion plans can be reused, however, and repeated occurrences of $T(\coma_i)$ and $M(\coma_{i\rightarrow i^{\prime}})$ should be counted only once for a total of: 
\begin{myitem}
\item[$-$] $  {\permu[n]{2}} $ \textit{transfers} of objects, and 
\item[$-$] $ {{\permu[n]{2}}\times\permu[n-2]{2}} $ \textit{transits} between all possible valid ordered pairs of $ \coma $.
\end{myitem}
Additional motion plans are needed for the initial move from $q_{\rm safe}^k$ and the return to it at the end of the process, introducing $ 2\times\permu[n]{2} $ transits:

>>>>

\vspace{-0.25in}
\begin{equation*}
{\permu[n]{2}} + {\permu[n]{2}}\times{\permu[n-2]{2}} + ... + {\permu[n]{2}}\times{\permu[n-2]{2}}\times{\permu[n-4]{2}}...\times{\permu[2]{2}} =\sum_{L=1}^{n/2} {\ \prod_{k=0}^{2L-1}{(n-k)}},
\vspace{-0.15in}
\end{equation*}
where $\permu[n]{k}$ is the $k$-permutations of $n$.

\begin{wrapfigure}{r}{2.4in}
    \vspace{-.5in}
	\centering
	\includegraphics[width=1.8in]{figures/dual_backtracking.PNG}
    \vspace{-.15in}
	\caption{Search tree for 4 objects. 
%	In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. 
	}
	\label{fig:backtracking}
    \vspace{-.3in}
\end{wrapfigure}
Motion plans can be reused, however, and repeated occurrences of $T(\coma_i)$ and $M(\coma_{i\rightarrow i^{\prime}})$ should be counted only once for a total of: 
\begin{myitem}
\item[$-$] $  {\permu[n]{2}} $ \textit{transfers} of objects, and 
\item[$-$] $ {{\permu[n]{2}}\times\permu[n-2]{2}} $ \textit{transits} between all possible valid ordered pairs of $ \coma $.
\end{myitem}
Additional motion plans are needed for the initial move from $q_{\rm safe}^k$ and the return to it at the end of the process, introducing $ 2\times\permu[n]{2} $ transits:

### 2018-10-29 05_approximation.tex
Bringing it down to the page limit

{\lemma [Perfect Matching]
Every candidate solution to a monotone dual-arm rearrangement problem comprises of a set of unordered object-to-arm assignments $ \scomaset $ that is also a perfect matching solution on $ \graph $.
}

As per the decomposition of the costs in Eq. \ref{eq:cost_function}, it follows that the $ \cost(\scomaset) $ corresponds to the cost of the transfers in the solution. Given the reduction to edge-matching, the solution to the minimum-weight perfect edge matching problem on such a graph would correspond to a $ \scomaset $ that optimizes the cost of \textit{transfers} of all the objects.

@@

A complete candidate solution to the problem now requires the sequence of~$ \coma $. By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. This is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.

{
\lemma [Tour]
Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous dual-arm rearrangement problem.
}

@@

>>>>

\vspace{-0.13in}
{\lemma [Perfect Matching]
Every candidate solution to a monotone dual-arm rearrangement problem comprises of a set of unordered object-to-arm assignments $ \scomaset $ that is also a perfect matching solution on $ \graph $.
}

As per the decomposition of the costs in Eq. \ref{eq:cost_function}, it follows that the $ \cost(\scomaset) $ is the cost of the transfers in the solution. The solution to the minimum-weight perfect edge matching problem on such a graph would correspond to a $ \scomaset $ that optimizes the cost of \textit{transfers} of all the objects.

@@

A complete candidate solution to the problem now requires the sequence of~$ \coma $. By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. This is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
\vspace{-0.1in}
{
\lemma [Tour]
Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous dual-arm rearrangement problem.
}

@@

\vspace{-0.1in}

### 2018-10-29 07_cost_bounds.tex
Bringing it down to the page limit

\commentadd{
\noindent \textbf{Note on bounds:} The proposed simplified model does not apply immediately to general configuration spaces, where the costs and collision volumes do not have the same nice properties of a planar disk setup. The experimental section, however, indicates that the benefits and speedups exist in these spaces as well.
}
% \rahul{this paragraph is phrased contradictorily. It makes sense if the first sentence is for asynchronous cases.}
% We note that the same can be said for a {\em synchronous} $2$-arm solution if
% when $c_t/c_{pd}$ is small. 
% Under the synchronization assumption, $C_{dual}^t$
% is no longer necessarily expected to be $\frac{C_{single}}{2}$ for large $n$. 
% Experiments in the next section indicate that improvements over single arm solutions in practical settings.

>>>>

\commentadd{
\noindent \textbf{Note on bounds:} Even though the proposed simplified model does not apply immediately costs and collision volumes in general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
}
% \rahul{this paragraph is phrased contradictorily. It makes sense if the first sentence is for asynchronous cases.}
% We note that the same can be said for a {\em synchronous} $2$-arm solution if
% when $c_t/c_{pd}$ is small. 
% Under the synchronization assumption, $C_{dual}^t$
% is no longer necessarily expected to be $\frac{C_{single}}{2}$ for large $n$. 
% Experiments in the next section indicate that improvements over single arm solutions in practical settings.

### 2018-10-29 08_evaluation.tex
Bringing it down to the page limit

\begin{wrapfigure}{r}{2.2in}
    \vspace{-.3in}
	\centering
		\includegraphics[width=1.1in,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
		\includegraphics[width=1.05in]{figures/kuka_benchmark2}
		\vspace{-.3in}
		\caption{\textit{Picker} and \textit{Manipulator} trials.}
		\label{fig:benchmarks}
    \vspace{-.25in}
\end{wrapfigure}
This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=1.9in]{figures/simple_picker_benchmark}
%	\includegraphics[width=1.8in]{figures/kuka_benchmark2}
%	\caption{The benchmarks: \textit{Simple Picker} and the \textit{General Manipulators} }
%	\label{fig:benchmarks}
%\end{figure}
In order to ensure monotonicity, the object starts and goals do not overlap. Uniform cuboidal objects simplify the grasping problem, though this is not a limitation of the methods. $ 50 $ random experiments were limited to $300s$ of computation time. The underlying $ \drrtstar $ motion planner is restricted to a max of $ 3s $ per plan.
A comparison point includes a random split method, which splits $ \objectset $ at random into two subsets and chooses an arbitrary ordering. Maximum of distances cost is compared to the single arm solution~\cite{193}. Computation times and success rates are reported. The trends in both experiments show that in the single-shot versions, exhaustive and \milp tend to time-out for larger $n$. Lazy variants scale much better for all the algorithms, and in some cases increase the success ratio due to retries. \algo has much better running time than exhaustive and \milp, and producing better and more solutions than random split. Overall, the results show a) our \milp succeeds more within the time limit than exhaustive, b) \algo scales the best among all the methods, and c) the cost of solutions from \algo is close to the optimal baseline, which is around half of the single arm cost.
% to demonstrate the gains from using multiple arms.  Overall, MILP scales better than exhaustive search, while finding optimal solutions. \algo scales better than the other methods, and finds high quality solutions. The lazy variants improve all the dual-arm methods.

@@

\begin{figure}[h]
\vspace{-0.2in}
	\centering
%	\includegraphics[width=2.1in]{figures/disk_solution}
%	\includegraphics[width=2.1in]{figures/disk_timing}
%	\includegraphics[width=2.1in]{figures/disk_more_solution}
%	\includegraphics[width=2.1in]{figures/disk_more_timing}
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_success}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_success}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_cost}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_cost}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_time}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_time}
	\vspace{-0.15in}
	\caption{\textit{Simple Picker} results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:disk}
\end{figure}

\begin{figure}[h]
\vspace{-0.2in}
	\centering
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_success}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_success}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_cost}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_cost}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_time}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_time}
	\vspace{-0.15in}
    \caption{\textit{\kuka}results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:kuka}
\end{figure}

>>>>

\begin{wrapfigure}{r}{2.2in}
    \vspace{-.6in}
	\centering
		\includegraphics[width=1.1in,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
		\includegraphics[width=1.05in]{figures/kuka_benchmark2}
		\vspace{-.3in}
		\caption{\textit{Picker} and \textit{Manipulator} trials.}
		\label{fig:benchmarks}
    \vspace{-.3in}
\end{wrapfigure}
This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=1.9in]{figures/simple_picker_benchmark}
%	\includegraphics[width=1.8in]{figures/kuka_benchmark2}
%	\caption{The benchmarks: \textit{Simple Picker} and the \textit{General Manipulators} }
%	\label{fig:benchmarks}
%\end{figure}
In order to ensure monotonicity, the object starts and goals do not overlap. Uniform cuboidal objects simplify the grasping problem, though this is not a limitation of the methods. $ 50 $ random experiments were limited to $300s$ of computation time. The underlying $ \drrtstar $ motion planner is restricted to a max of $ 3s $ per plan.
A comparison point includes a random split method, which splits $ \objectset $ at random into two subsets and chooses an arbitrary ordering. Maximum of distances cost is compared to the single arm solution~\cite{193}. Computation times and success rates are reported. The trends in both experiments show that in the single-shot versions, exhaustive and \milp tend to time-out for larger $n$. Lazy variants scale much better for all the algorithms, and in some cases increase the success ratio due to retries. \algo has much better running time than exhaustive and \milp, and producing better and more solutions than random split. Overall, the results show a) our \milp succeeds more within the time limit than exhaustive, b) \algo scales the best among all the methods, and c) the cost of solutions from \algo is close to the optimal baseline, which is around half of the single arm cost.
% to demonstrate the gains from using multiple arms.  Overall, MILP scales better than exhaustive search, while finding optimal solutions. \algo scales better than the other methods, and finds high quality solutions. The lazy variants improve all the dual-arm methods.

@@

\begin{figure}[h]
\vspace{-0.2in}
	\centering
%	\includegraphics[width=2.1in]{figures/disk_solution}
%	\includegraphics[width=2.1in]{figures/disk_timing}
%	\includegraphics[width=2.1in]{figures/disk_more_solution}
%	\includegraphics[width=2.1in]{figures/disk_more_timing}
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2in]{figures/results/4_sp_ms_success}
	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_success}
	\includegraphics[width=2in]{figures/results/4_sp_ms_cost}
	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_cost}
	\includegraphics[width=2in]{figures/results/4_sp_ms_time}
	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_time}
	\vspace{-0.15in}
	\caption{\textit{Simple Picker} results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:disk}
\end{figure}

\begin{figure}[h]
\vspace{-0.2in}
	\centering
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2in]{figures/results/2_kuka_ms_success}
	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_success}
	\includegraphics[width=2in]{figures/results/2_kuka_ms_cost}
	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_cost}
	\includegraphics[width=2in]{figures/results/2_kuka_ms_time}
	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_time}
	\vspace{-0.15in}
    \caption{\textit{\kuka}results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:kuka}
\end{figure}
